NIRCam Calibration Plan

### 2016-11-26 ms.tex
I added a plot to illustrate the proposed NIRCam sensitivity ladder. Still needs a legend.

\begin{table}
\centering
\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
\begin{tabular}{lrrrrrrr}
\hline \hline
Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter  & t$_{exp}$\\
\hline \hline
1		& Direct Calibrator\tablenotemark{a}	& G2 V 			& -1.49		& On	&	32$\times$32	& F466N	& \\
2		& Medium Calibrator				& G2 V			& 12  		& On  &	32$\times$32	& F466N  &  \\
3		& Medium Calibrator				& G2 V			& 6  			& Off &	32$\times$32	& F466N  &  \\
4		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F466N  &  \\
5		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F444W  &  \\
6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Array  	& F444W  &  \\
\hline
\end{tabular}
\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, Sirius, $\alpha$ Cen A or Vega.}
\vspace{0.05in}
\end{table}

>>>>

\begin{table}
\centering
\caption{Conversion from Directly Calibrated Source to Deep Calibrator}\label{tab:clusterProp}
\begin{tabular}{lrrrrrrr}
\hline \hline
Step		& Source						& Spectral Type	& K Mag		& ND Filter		& Subarray	& Filter  & t$_{exp}$\\
\hline \hline
1		& Direct Calibrator\tablenotemark{a}	& A1 V- G2 		& -1.35		& On	&	32$\times$32	& F466N	& \\
2		& Medium Calibrator				& G2 V			& 12  		& On  &	32$\times$32	& F466N  &  \\
3		& Medium Calibrator				& G2 V			& 6  			& Off &	32$\times$32	& F466N  &  \\
4		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F466N  &  \\
5		& Faint Calibrator				& G2 V			& 16 			& Off &	32$\times$32	& F444W  &  \\
6		& Faint Calibrator				& G2 V			& 16 			& Off &	Full Array  	& F444W  &  \\
\hline
\end{tabular}
\tablenotetext{a}{Any directly calibrated bright source such as the MSX calibrators \citep{price2004msxCal}, Sirius, $\alpha$ Cen A or Vega.}
\vspace{0.05in}
\end{table}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.7\columnwidth]{sensitivity_ladder.pdf}
\caption{Sensitivity ladder going from a narrowband, sub-array, neutral density filter observation of Sirius all the way to a wide band, full array, non-neutral density filter of a faint calibrator.}\label{fig:sensitityLadder}
\end{figure}
